---
title: "Test_Git"
output: html_notebook
---

Just operating a few tests and performing versioning control.
Let's tray some cleaning and data manipulation.
This notebook follows the exercise proposed by **R Programming 101** Youtube channel.

Basically we will use some features of **tidyverse** package. If you not have it, you can install it with the command commented bellow.

```{r}
#install.packages("tidyverse")
library(tidyverse)
```

We will work with Starwars data set, as an example to operate some changes. The aim is to simplify it according to ours needs.

```{r}
sw <- starwars
```

With glimpse() function, from dplyr(), we can see the data set's structure: how many rows ans columns, and the amount and type of the variables.

```{r}
glimpse(sw)
```

Using select() and rename(), we can change the structure of the data set into one more useful to meet our goals, selecting and renaming some variables.

Also, with na.omit() we are omitting the missing values and with mutate() we will create a new variable trough a previous one.

And finally, we rename the output of the variable gender and created a new variable called size, witch we choose to naming it as big or small, according to certain conditions.

```{r}
sw <- starwars %>%
  select(name, height, mass, gender) %>%
  rename(weigth = mass) %>%
  na.omit() %>%
  mutate(height = height/100) %>%
  filter(gender %in% c("male","female")) %>%
  mutate(gender = recode(gender,
                         male = "m",
                         female = "f")) %>%
  mutate(size = height >1 & weigth > 75,
         size = if_else(size == TRUE, "big", "small"))
```

```{r}
glimpse(sw)
```

```{r, error=TRUE}
summary(sw$height)
```

```{r}
summary(sw$weigth)
```


And that's all for now.
